Let's talk about Thurstone & Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2025-03-31 paper2.qmd
section:4.2; process:write

$$
S_{I} = \begin{bmatrix}
i_{(1)} \\
i_{(2)} \\
\vdots \\
i_{(h)} \\
\vdots \\
i_{(i)} \\
\vdots \\
i_{(nI)}
\end{bmatrix} ; \;
S_{J} = \begin{bmatrix}
j_{(1)} \\
j_{(2)} \\
\vdots \\
j_{(j)} \\
\vdots \\
j_{(nJ)}
\end{bmatrix} ; \;
S_{IA} = \begin{bmatrix}
ia_{(1)} \\
ia_{(2)} \\
\vdots \\
ia_{(ia)} \\
\vdots \\
ia_{(nI \cdot nA)} \\
\end{bmatrix} ; \;
S_{JK} = \begin{bmatrix}
jk_{(1)} \\
jk_{(2)} \\
\vdots \\
jk_{(jk)} \\
\vdots \\
jk_{(nJ \cdot nK)} \\
\end{bmatrix}
$$ {#eq-mat21}

@@

$$
S = \begin{bmatrix}
s_{(1)} \\
s_{(2)} \\
\vdots \\
s_{(s)} \\
\vdots \\
s_{(n)} \\
\end{bmatrix}
$$ {#eq-mat25}

@@

However, because CJ experiments rarely use the exhaustive pairing of the sampled judgments, judges, stimuli, and individuals --due to concerns about the practical feasibility of the comparison task, like in @Boonen_et_al_2020 [p. 5]-- a realistic scenario must also account for judges comparing only specific stimuli from certain individuals.

>>>>

$$
S_{I} = \begin{bmatrix}
i_{(1)} \\
\vdots \\
i_{(h)} \\
\vdots \\
i_{(i)} \\
\vdots \\
i_{(nI)}
\end{bmatrix} ; \;
S_{J} = \begin{bmatrix}
j_{(1)} \\
\vdots \\
j_{(j)} \\
\vdots \\
j_{(nJ)}
\end{bmatrix} ; \;
S_{IA} = \begin{bmatrix}
ia_{(1)} \\
\vdots \\
ia_{(ia)} \\
\vdots \\
ia_{(nI \cdot nA)} \\
\end{bmatrix} ; \;
S_{JK} = \begin{bmatrix}
jk_{(1)} \\
\vdots \\
jk_{(jk)} \\
\vdots \\
jk_{(nJ \cdot nK)} \\
\end{bmatrix}
$$ {#eq-mat21}

@@

$$
S = \begin{bmatrix}
s_{(1)} \\
\vdots \\
s_{(s)} \\
\vdots \\
s_{(n)} \\
\end{bmatrix}
$$ {#eq-mat25}

@@

However, because CJ experiments rarely use the exhaustive pairing of sampled judges, stimuli, and individuals --due to concerns about the practical feasibility of the comparison task, like in @Boonen_et_al_2020 [p. 5]-- a realistic scenario must also account for judges comparing only specific stimuli from certain individuals.
